---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# datafairy

<!-- badges: start -->
<!-- badges: end -->

<img src="man/figures/logo.svg" align="right" height="139" />

The datafairy is grants you basic data handling wishes: The packages includes helper functions for creating minimaistic codebooks or describing numeric and factor data.  


## Installation

You can install the development version of datafairy from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lmwidmayer/datafairy")
```

## Example

This is example shows how to make a codebook template from a flat dataframe:

```{r example}
library(datafairy)

## create a codebook
df <- data.frame(
  id = 1:4,
  condition = factor(LETTERS[1:4]),
  score = c(2.1, 4.0, NA, 3.3)
) # a dataframe that you want to document
cb <- mini_cb(df, auto.type = TRUE, content.type = TRUE)

print(cb)
```

Write the codebook `cb` to a tabular file format or `json` and populate it with the descriptions of your data set:

- `NAME`: The column/ variable name of the input dataframe.
- `TYPE`: Data type of the variable: If `auto.type = TRUE`, the function will use `R`'s data types.
- `UNIT`: Unit of measurement.
- `DESCRIPTION`: Describe what the variable contains.
- `ANNOTATION`: Further comments on the variable.

Note that `content.type = TRUE` adds a row with the name `CONTENT` in which you can describe to which data set this codebook belongs.  

<!-- devtools::build_readme() -->

