---
title: "overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(datafairy)
```

## Example for mini_cb()

This example shows how to make a codebook template from a flat dataframe:

```{r example}
## create a dummy dataframe
df <- data.frame(
  id = 1:4,
  condition = factor(LETTERS[1:4]),
  score = c(2.1, 4.0, NA, 3.3)
) # a dataframe that you want to document
cb <- mini_cb(df, auto.type = TRUE, content.type = TRUE)

print(cb)
```

Write the codebook `cb` to a tabular file format or `json` and populate it with the descriptions of your data set:

- `NAME`: The column/ variable name of the input dataframe.
- `TYPE`: Data type of the variable: If `auto.type = TRUE`, the function will use `R`'s data types.
- `UNIT`: Unit of measurement.
- `DESCRIPTION`: Describe what the variable contains.
- `ANNOTATION`: Further comments on the variable.

Note that `content.type = TRUE` adds a row with the name `CONTENT` in which you can describe to which data set this codebook belongs.  


## Example for describe()

Using the dummy dataframe from the previous section, this example shows how to describe data vectors.  

```{r}
# use dummy dataframe from previous example
tab.condition <- describe(df$condition)
print(tab.condition)
```

```{r}
# use dummy dataframe from previous example
tab.score <- describe(df$score, na.rm = TRUE)
print(tab.score)
```
